Hydra Battles in Coq

### 2020-11-24 doc/part-hydras.tex
simplifying the namespace

\label{sect:hardy}
In order to give an idea of the complexity of the functions  $L_\alpha$s, we compare them with a better known family of functions, the so called \emph{Wainer-Hardy hierarchy} of fast growing functions,
presented for instance in~\cite{Promel2013}. 
\index{Maths!Hardy hierarchy}

@@

For instance, the following theorem states that, if $\gamma$ is the sum of a limit ordinal $\beta$ and a finite ordinal $n$, and $\beta$ is a fixpoint of
$\phi_\alpha$, then $\psi(\alpha,\gamma)=\phi_\alpha(\gamma+1)$.

@@

\chapter{Appendices}

\bibliographystyle{alpha}
\bibliography{thebib}

\section{Index}

\begin{table}[h]
  \centering
  \begin{threeparttable}
    \caption{Main types and type classes}
\begin{tabular}{|c|c|c|l|}
\hline
Name & Description& Page \\\hline
Battle & type class of battle types & \pageref{types:Battle} \\
E0 & (well formed) ordinals below $\epsilon_0$ & \pageref{types:E0}\\
Hvariant & variants for proving termination of hydra battles & \pageref{sect:hvariant-def} \\
Hydra & tree-like representation of hydras & \pageref{types:Hydra} \\
Hydrae & finite sequences of hydras & \pageref{types:Hydrae} \\
ON & ordinal  notations & \pageref{types:ON} \\
ON\_for & comparison of an ordinal notation with Schütte's model &  \pageref{types:ON-for}\\
ON\_iso & isomorphism of ordinal notations  & \pageref{types:ON-iso}\\

Ord & countable ordinals (after Schütte) & \pageref{types:Ord} \\
ppT1 & pretty printed version of T1 & \pageref{types:ppT1} \\
SubON & comparison of ordinal notations & \pageref{types:SubON} \\
T1 & ordinal terms below $\epsilon_0$ & \pageref{types:T1} \\
T2 & ordinal terms below $\Gamma_0$ & \pageref{types:T2} \\
WO & well orders (Schütte's definition) & \pageref{types:WO} \\
\hline
\end{tabular}
\end{threeparttable}
\end{table}

\begin{table}[h]
  \centering
  \begin{threeparttable}
    \caption{Main functions and constants}
\begin{tabular}{|r | c|c|c|c|l|}
\hline
Name & Gallina & Math & Description & Page \\ \hline
canon & canon alpha i & $\canonseq{\alpha}{i}$& canonical sequence & \pageref{Functions:canon}\\
canonS & canonS alpha i & $\canonseq{\alpha}{i+1}$& helper for canon & \pageref{Functions:canonS}\\
F\_ & F\_ alpha n & $F_\alpha(n)$ & Wainer's \texttt{F} fast growing hierarchy & \pageref{Functions:F-alpha} \\
H\_ & H\_ alpha n & $H_\alpha(n)$ & Hardy's \texttt{H} fast growing hierarchy & \pageref{Functions:H-alpha} \\
iterate & iterate $f$ $n$ $x$ & $f^{(n)}(x)$ & functional iteration & \pageref{Functions:iterate} \\
L\_ & L\_ alpha k & $L_\alpha(k)$ & final step of a standard path & \pageref{Functions:L-alpha} \\
succ & succ alpha & & successor & \pageref{Functions:succ-T1}, \pageref{Functions:succ-sch} \dots \\
zero:Ord & & $0$ & the least ordinal (Schütte's model) & \pageref{Constants:zero:Ord} \\

\hline
\end{tabular}
\end{threeparttable}
\end{table}

\begin{table}[h]
  \centering
  \begin{threeparttable}
    \caption{Main predicates}
\begin{tabular}{|r | c|c|c|c|l|}
\hline
Name & Gallina&Math& Description& Page \\\hline
\texttt{lt : T1->T1->Prop}& lt alpha beta & $\alpha < \beta$& strict order on type \texttt{T1} \tnote{1} & \pageref{Predicates:lt-T1}\\
\texttt{LT: T1->T1->Prop}& alpha o< beta & $\alpha < \beta$& strict order on type \texttt{T1}   \tnote{2} & \pageref{Predicates:LT-T1}\\
\texttt{Lt : E0->E0->Prop} & alpha o< beta & $\alpha < \beta$& strict order on type \texttt{E0} \tnote{3} & \pageref{Predicates:Lt-E0} \\
\texttt{nf: T1->Prop} & \texttt{nf alpha} && alpha is in Cantor normal form & \pageref{Predicates:nf-T1}\\
\hline
\end{tabular}
\begin{tablenotes}
  \item[1] This order is total, but not well-founded, because of not well formed terms.
\item[2] Restriction of \texttt{lt} to terms in normal form; this order is partial, but well-founded.
\item[3] This order is total \emph{and} well-founded.
\end{tablenotes}
\end{threeparttable}
\end{table}

\vspace{4pt}
\begin{table}[h]
  \centering
  \begin{threeparttable}
    \caption{Infix notations}
\begin{tabular}{|c|c|c|c|l|}
\hline
Name & Gallina&Math& Description& Page \\\hline
 \texttt{on\_lt} & \texttt{alpha o< beta}&$\alpha<\beta$& ordinal inequality \tnote{1} & \pageref{sect:on-lt-notation}\\
 \texttt{on\_le} & \texttt{alpha o<= beta}&$\alpha\leq\beta$& ordinal inequality & \pageref{sect:on-lt-notation}\\
\texttt{plus} & \texttt{alpha + beta} & $\alpha + \beta$ & ordinal addition & \pageref{sect:infix-plus-T1}, \dots\\
\texttt{oplus} & \texttt{alpha o+ beta} & $\alpha \oplus \beta$ & Hessenberg sum & \pageref{sect:infix-oplus} \\
\texttt{round} & \texttt{h -1-> h'} & & one round of a battle & \pageref{sect:infix-round} \\
\texttt{rounds} & \texttt{h -+-> h'} & & one or more  rounds of a battle & \pageref{sect:infix-rounds} \\
\texttt{round\_star} & \texttt{h -*-> h'} & & any number of rounds of a battle & \pageref{sect:infix-rounds} \\

\hline
\end{tabular}

\begin{tablenotes}
 \item [1]
Some notations may belong to several scopes. For instance, ``\texttt{o<}'' is
bound in \texttt{ON\_scope}, \texttt{E0\_scope}, \texttt{t1\_scope}, etc., and locally in several libraries.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}[h]
  \centering
  \begin{threeparttable}
    \caption{Other notations}
\begin{tabular}{|c|c|c|c|l|}
\hline
Name & Gallina&Math& Description& Page \\\hline
F & \texttt{F $n$} & $n$ & The $n$-th finite ordinal &  
\pageref{sect:notation-F}, \pageref{sect:notation-F-sch}\\ 
FS & \texttt{FS $n$} & $n+1$ & The $n+1$-th finite ordinal  \tnote{2} &  
\pageref{sect:notation-FS}\\ 
omega & \texttt{omega} & $\omega$ &   the first infinite ordinal   & \pageref{sect:notation-omega}, \pageref{sect:omega-T1}, \pageref{sect:omega-notation2}, \dots\\
phi0     & \texttt{phi0 alpha} & $\phi_0(\alpha),\; \omega^\alpha$&exponential of base $\omega$ & \pageref{sect:notation-phi0}\\

\hline
\end{tabular}

\begin{tablenotes}
  \item [2] Note that there exist also various coercions from \texttt{nat} to types of ordinal. Depending on the current scope and  \coq's syntactic analysis algorithm, \texttt{F} may be left implicit.
\end{tablenotes}
  \end{threeparttable}

\end{table}

\printindex

% \section{Main notations}

% \subsubsection*{Intervals}

% Let $\leq$ be a total order on a type $A$. The intervals $\{k\in A| i\leq k\leq j\}$ is written $[i,j]$. Likewise, $\{k\in A| i\leq k<j\}$ is written
% $[i,j[$.

\end{document}

>>>>

\label{sect:hardy}
In order to give an idea of the complexity of the functions  $L_\alpha$s, we compare them with a better known family of functions, the so called \emph{Wainer-Hardy hierarchy} of fast growing functions,
presented for instance in~\cite{Promel2013}. 
\index{Maths!Hardy Hierarchy}

@@

For instance, the following theorem states that, if $\gamma$ is the sum of a limit ordinal $\beta$ and a finite ordinal $n$, and $\beta$ is a fixpoint of
$\phi(\alpha)$, then $\psi(\alpha,\gamma)=\phi_\alpha(\gamma+1)$.

@@
